Model Search in Relational Domains

### 2016-10-23 algorithm.tex
proof-reading all section
section 4 proof-read

program in the form of the set of its abstract transformers

@@

$\abs(\trail)=\top$ if $\trail$ is the empty sequence $\langle\rangle$.

@@

abstract value $\top$.  The procedure $\deduce$ (detailed in
Section~\ref{sec:deduce}) computes a greatest fixed point over the

@@

taking into account the current decision.  The model search phase

@@

In the latter case the algorithm enters in the $\analyzeconflict$ 
phase (see Section~\ref{sec:conflict}) to learn the reason for the conflict.   There can be multiple
incomparable reasons for conflict.
% \pscmt{do you have to explain this here?} -- based on the choice of Unique
%Implication Point (UIP)~\cite{cdcl}.  
ACDCL heuristically chooses one reason $\conflictset$ and learns it 
by adding it as an abstract transformer to $\abstransset$. The algorithm 
backtracks by removing the content of $\trail$ up to a point where it does not 
conflict with $\conflictset$.  ACDCL then performs deductions with the learnt 
transformer.  If $\analyzeconflict$ returns $\false$, then no further
backtracking is possible.  Thus, the $\formula$ is unsatisfiable
and ACDCL return \textsf{safe}.

>>>>

program in the form of a set of abstract transformers

@@

$\abs(\trail)=\top$ if $\trail$ is an empty sequence $\langle\rangle$.

@@

abstract value $\top$.  The procedure $\deduce$ (details in
Section~\ref{sec:deduce}) computes a greatest fixed-point over the

@@

based on the current decision.  The model search phase

@@

In the latter case the algorithm enters in the $\analyzeconflict$ 
phase (see Section~\ref{sec:conflict}) to learn the reason for the conflict.   There can be multiple
incomparable reasons for conflict.
% \pscmt{do you have to explain this here?} -- based on the choice of Unique
%Implication Point (UIP)~\cite{cdcl}.  
ACDCL heuristically chooses one reason $\conflictset$ and learns it 
by adding it as an abstract transformer to $\abstransset$. The analysis 
backtracks by removing the content of $\trail$ up to a point where it does not 
conflict with $\conflictset$.  ACDCL then performs deductions with the learnt 
transformer.  If $\analyzeconflict$ returns $\false$, then no further
backtracking is possible.  Thus, the safety equation $\formula$ is unsatisfiable
and ACDCL return \textsf{safe}.

### 2016-10-23 paper.tex
section 4 proof-read

%===============================================================================
\begin{abstract}
%===============================================================================
%
\emph{Abstract Conflict-Driven Clause Learning} (ACDCL) is a generalisation
of the well-known CDCL algorithm used in SAT solvers.
%
\Omit {  ACDCL alternates between a model search, which
performs over-approximate deduction with constraint propagation, and a
conflict analysis, which performs under-approximate abduction with heuristic
choice.
}
%
It has been successfully used with non-relational abstract domains, such
as intervals, to improve the performance of a floating-point decision
procedure.  Whereas the propositional reasoning of SAT 
solvers can be lifted easily from the Boolean lattice to other 
non-relational domains, application to relational domains is 
challenging because of the relational properties of deductions.
%
In this paper, we present non-trivial liftings of the model search and
conflict analysis algorithms of SAT solvers to relational abstract domains.  We have
implemented these algorithms inside the 2LS verification tool and
instantiated our analyser with a template polyhedra domain to check safety
properties of C programs.  We~evaluate the performance of our analyser 
compared to a program verifier that uses propositional solvers and
an abstract interpretation tool.
%static analyser based on abstract interpretation.
%
\Omit {
on a set of benchmarks drawn from bit-vector regression 
in SV-COMP'16, bit-precise software models of hardware 
circuits auto-generated from v2c tool, and several 
bounds checking benchmarks 
}
We observe a reduction of two orders of magnitude in the number of 
decisions and conflict analyses compared to a SAT 
solver and higher precision compared to an abstract interpreter. 
\Omit{
along with stronger deductions and learnt clauses aided by the richer
abstract domains.
}
%
\end{abstract}

>>>>

%===============================================================================
\begin{abstract}
%===============================================================================
%
\emph{Abstract Conflict-Driven Clause Learning} (ACDCL) is a generalisation
of the well-known CDCL algorithm used in SAT solvers.
%
\Omit {  ACDCL alternates between a model search, which
performs over-approximate deduction with constraint propagation, and a
conflict analysis, which performs under-approximate abduction with heuristic
choice.
}
%
It has been successfully used with non-relational abstract domains, such
as intervals, to improve the performance of a floating-point decision
procedure.  Whereas the propositional reasoning of SAT 
solvers can be lifted easily from the Boolean lattice to other 
non-relational domains, application to relational domains is 
challenging because of the relational properties of deductions.
%
In this paper, we present non-trivial liftings of the model search and
conflict analysis algorithms of SAT solvers to relational abstract domains.  We have
implemented these algorithms inside the 2LS verification tool and
instantiated our analyser with a template polyhedra domain to check safety
properties of C programs.  We~evaluate the performance of our analyser 
compared to a program verifier that uses propositional solvers and
an abstract interpretation tool.
%static analyser based on abstract interpretation.
%
\Omit {
on a set of benchmarks drawn from bit-vector regression 
in SV-COMP'16, bit-precise software models of hardware 
circuits auto-generated from v2c tool, and several 
bounds checking benchmarks 
}
We observe a reduction of two orders of magnitude in the number of 
decisions, propagations, and conflicts compared to a SAT 
solver and higher precision compared to an abstract interpreter. 
\Omit{
along with stronger deductions and learnt clauses aided by the richer
abstract domains.
}
%
\end{abstract}
